---
title: "BAYQUEN-FA9-EXERCISES18.1"
author: "Christopher Bayquen"
date: "2023-05-01"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 18.1.1

An analogue signal received at a detector, measured in microvolts, is normally
distributed with `mean of 200` and `variance of 256`
```{r}
mean <- 200
std <- sqrt(256)
```

**a. What is the probability that the signal will `exceed 224 ðœ‡V`?**
```{r}
prob <- 1 - pnorm(224, mean, std)
prob
```

**b. What is the probability that it will be between `186ðœ‡V and 224 ðœ‡V`?**
```{r}
prob <- pnorm(224, mean, std)-pnorm(186, mean, std)
prob
```

**c. What is the micro voltage below which 25% of the signals will be?**
```{r}
prob <- qnorm(0.25,mean,std)
prob
```

**d. What is the probability that the signal will be less than `240 ðœ‡V`, given that it is `    larger than 210 ðœ‡V`? **
```{r}
prob1 <- pnorm(240, mean, std) - pnorm(210, mean, std)
prob2 <- 1-pnorm(210, mean, std)
prob <- prob1/prob2
prob

```

**e. Estimate the interquartile range.**
```{r}
range1 <- qnorm(0.25,mean,std)
range2 <- qnorm(0.75,mean, std)

cat("The interquartile range is between ~", range1, "and", range2)
```

**f. What is the probability that the signal will be `less than 220 ðœ‡V`, given that it is `larger than 210 ðœ‡V`?**
```{r}
prob1 <- pnorm(220, mean, std) - pnorm(210, mean, std)
prob2 <- 1-pnorm(210, mean, std)
prob <- prob1/prob2
prob

```

**g. If we know that a received signal is `greater that 200 ðœ‡V`, what is the probability that is in fact `greater than 220 ðœ‡V`?**
```{r}
prob1 <- 1-pnorm(200,mean,std)
prob2 <- 1-pnorm(220,mean,std)
prob <- prob2/prob1
prob
```

## 18.1.2
A manufacturer of a particular type of computer system is interested in improving its customer support services. As a first step, its marketing department has been charged with the responsibility of summarizing the extent of customer problems in terms of system failures. Over a period of six months, customers were surveyed and the amount of downtime (in minutes) due to system failures they had experienced during the previous month was collected. The average downtime was found to be 25 minutes and a variance of 144. If it can be assumed that downtime is normally distributed:
```{r}
mean <- 25
std <- sqrt(144)
```

**a. obtain bounds which will include 95% of the downtime of all the customers**
```{r}
bound1 <- qnorm(0.025, mean, std)
bound2 <- qnorm(0.975, mean, std)

cat("95% of the downtime of all the customers is between ~", bound1, "minutes and ", bound2, "minutes")
```
**b. obtain the bound above which 10% of the downtime is included**
```{r}
upperbound <- qnorm(0.90,mean,std)
cat("the top 10% of the downtime of the customers is~", upperbound, "minutes")
```
