---
title: "BAYQUEN-FA8"
author: "Christopher Bayquen"
date: "2023-04-30"
output: html_document
---

## 16.1.1
In Example 16.3 with ğœ† = 4 per minute, use R to obtain:

**a) P(T â‰¤ 0.25) = P(time between submissions is at most 15 seconds);**
```{r}
lambda <- 4 #4 per minute
time <- 0.25

prob <- pexp(time,lambda)
prob

```

**b) P(T > 0.5) = P(time between submissions is greater than 30 seconds);**

```{r}
lambda <- 4 #4 per minute
time <- 0.5

prob <- pexp(time,lambda)
prob

```

**c) P(0.25 < T < 1) = P(time between submissions is between 15 seconds and 1 minute).**

```{r}
lambda <- 4  #4 per minute
time1 <- 0.25
time2 <- 1

prob <- (pexp(time2,lambda))- (pexp(time1,lambda))
prob

```

## 16.1.3
The average rate of job submissions in a computer center is 2 per minute. If
it can be assumed that the number of submissions per minute has a Poisson
distribution, calculate the probability that:

**a) more than two jobs will arrive in a minute**
```{r}
lambda <- 2                   #average rate of job submissions in a computer center
prob_less2 <- ppois(2,lambda) #probability that less than 2 submissions are received
prob_more2 <- 1-prob_less2    #probability that more than 2 submissions are received
prob_more2


```

**b) at least 30 seconds will elapse between any two jobs**
```{r}
lambda <- 2/60 #converted rate of submission per second
prob <- 1 - pexp(30, lambda)
prob
```


**c) less than 30 seconds will elapse between jobs**
```{r}
lambda <- 2/60 #converted rate of submission per second
prob1 <- ppois(0,lambda*30)
prob2 <- 1-prob1

prob2
```

**d)  a job will arrive in the next 30 seconds, if no jobs have arrived in the last30 seconds.**
```{r}
lambda <- 2/60  #converted rate of submission per second

prob <- dpois(1, lambda*30) 
prob
```

## 16.1.7
A website receives an average of 15 visits per hour, which arrive following a
Poisson distribution.

**a) Calculate the probability that at least 10 minutes will elapse without a visit**
```{r}
lambda <- 15/60 #average visits per minute
```

b) What is the probability that in any hour, there will be less than eight visits?

c) Suppose that 15 minutes have elapsed since the last visit, what is the probability 
that a possibility that a visit will occur in the next 15 minutes.

d) Calculate the top quartile, and explain what it means.