---
title: "BAYQUEN-LABWORK-15.1"
author: "Christopher Bayquen"
date: "2023-04-17"
output: html_document
---


## 15.1.1

A machine produces memory sticks of varying lengths, distributed uniformly between 2 and 12 mm. Memory sticks longer than 10 mm do not meet the design criterion, and must be scrapped.

(a) Calculate the probability that a memory stick will be scrapped.
(b) Simulate 50 memory stick lengths and obtain a histogram of the simulated values. Calculate the simulated mean and variance.

**A. Probability that a memory stick will be scrapped:**
```{R}
# 2 memory sticks are greater than 10mm in length
# there are 10 different memory sticks in total
P_scrapped <- (2/10)
P_scrapped
```

**B. Simulation of 50 memory stick lengths**

```{r}
#50 memory stick lengths simulation
lengthSim <- runif(50,2,12)

#histogram plot of simulation
hist(lengthSim, breaks = 10, xlab = "Length in mm", ylab = "Frequency")

#mean and variance calculations
mean <- mean(lengthSim)
variance <- var(lengthSim)

cat("Simulated mean of lengths:", mean)
cat("Simulated variance of lengths :", variance)
```

## 15.1.2
Students in an electronic engineering laboratory measure current in using an ammeter. Due to several random factors, the measurement X follows the pdf:

```f(x)= 0.025x + b , 2 < x < 6```

(a) Show that, for this to be a genuine probability density, b = 0.15.
(b) Find the probability that the measurement of the current exceeds 3 A.
(c) Find E(X)

**A. Proof that b = 0.15**
```{r}
pdf <- function(x) {0.025*x + b}

```

##  15.1.3

In a radio communications system, the phase difference X between the transmitter and receiver is modeled as having a uniform density in [âˆ’ðœ‹,+ðœ‹]. Find
P(X â‰¤ 0) and P(X â‰¤ ðœ‹âˆ•2)].